

```{r}
pacman::p_load(tidyverse)
```

```{r}
df <- read_csv("data/pretrain_1_raw.csv")
```


$$OD = -1 \cdot log\left(\dfrac{x}{\dfrac{1}{N}\sum{x}}\right)$$
$$BL=I_D=I_Se^{-\mu_aL}$$
Photon travel is different so we sum over all the paths. We approximate that by approximating the sum as a function $G(\mu_s,P)$. $<L>$ as avg pathlength.

We then approximate the pathlength with the short-detector separation distance. DPF is greater than 1 and is the multiplier on $\rho$ to say how much longer it is on average.

Then the equation is $I_D(t) =I_SG(\mu_S',\rho)e^{-\mu_{a\Phi}DPF*\rho}$ and there is much of that that is constant. Therefore, we end up with:

$$mBL: \dfrac{I_D(t)}{I_D(t=0)}=e^{-\Delta\mu_a(t)}\cdot DPF\cdot \rho$$

$\rho$ and $DPF$ are known along with $I_D(t)$ and $I_D(t=0)$ so we can solve for $\Delta\mu_a(t)$.

$\Delta\mu_a(t)$ is the variation of absorbance so we're very much interested in this.

$$\Delta OD=-log\left(\dfrac{I(t)}{I^0}\right)\approx \langle L\rangle\Delta \mu_ a(t)+\left(\dfrac{\mu_a^0}{\mu_s'^0}\right)\cdot \langle L\rangle\Delta \mu_ a'(t)\approx \langle L\rangle\Delta \mu_a(t)$$

$$\Delta \mu_a(t) = \dfrac {\Delta OD}{\langle L\rangle}=\dfrac{\Delta OD}{DPF\cdot\rho}$$

$$\langle L \rangle = \dfrac{\Delta OD^0}{\Delta \mu_a}$$

    hbo   hb
760 586	  1548.52000000000
850 1058	691.320000000000

abs_coef =
[[HbO2(freq1), Hb(freq1)],
 [HbO2(freq2), Hb(freq2)]]

abs_coef * distance_at_channel * dpf
pseudo-inverse matrix transform of the above

Matrix multiplying with the inverse is like division: $A \times A^{-1}=1$.

EL = abs_coef * distances[ii] * ppf
iEL = linalg.pinv(EL)

raw._data[[ii, ii + 1]] = iEL @ raw._data[[ii, ii + 1]] * 1e-3

The above does the following:
- Takes the hbo and hbr channel and divides it by $\rho$ and 1000

Why use inverse matrix for multiplication: 
- We cannot divide matrices
- $XA=B$, solving for X in the previous, we cannot just divide by A
- $XI=BA^{-1}=X$ gives us the correct result - will not work if $BA$ do not have the proper dimensions
- We have to place $A^{-1}$ at the proper spot because matrix multiplication is sequence determinant
  - $AX=B\Rightarrow A^{-1}X=A^{-1}B$
- $(BA)^{-1}=A^{-1}B^{-1}$

$$\begin{bmatrix}\Delta c_{HbO}(t) \\ \Delta c_{HbR}(t)\end{bmatrix} 
= 
\begin{bmatrix}\alpha_{HbO}(\lambda_1) & \alpha_{HbR} (\lambda_1) \\ \alpha_{HbO} (\lambda_2) & \alpha_{HbR} (\lambda_2) \end{bmatrix}^{-1}
\begin{bmatrix}\Delta A(t, \lambda_1) \\ \Delta A(t, \lambda_2)\end{bmatrix}
\dfrac{1}{l\times d}$$

$$\dfrac{1}{hbo760\cdot hbr850 - hbr760\cdot hbo850}\begin{bmatrix}hbr850&-hbr760\\-hbo850&hbo760\end{bmatrix}\times\begin{bmatrix}760 & 0.9&...&-0.2\\850&-0.03&...&0.2\end{bmatrix}$$

$$\begin{bmatrix}hbo760&hbr760\\hbo850&hbr850\end{bmatrix}$$


```{r}
pacman::p_load(matlib, dplR, qdap)

freqs = c(760, 850)
dpf = 6
hb_ext = c(586, 1058, 1548.52, 691.32)
hb_abs = hb_ext * 0.2303
hbo_760 = hb_abs[1]
hbo_850 = hb_abs[2]
hbr_760 = hb_abs[3]
hbr_850 = hb_abs[4]

mu = 

p = read_csv("data/distances.csv") %>% 
  select(p = "0") %>% 
  mutate(channel = colnames(df %>% select(matches("S\\d*")))) %>% 
  select(channel, p)

df_od <- df %>% 
  select(-c("X1", "time")) %>% 
  mutate(across(where(is.numeric), ~ -log(.x / mean(.x))))
```
$$\begin{bmatrix}\Delta c_{HbO}(t) \\ \Delta c_{HbR}(t)\end{bmatrix} 
= 
\begin{bmatrix}\alpha_{HbO}(\lambda_1) & \alpha_{HbR} (\lambda_1) \\ \alpha_{HbO} (\lambda_2) & \alpha_{HbR} (\lambda_2) \end{bmatrix}^{-1}
\begin{bmatrix}\Delta A(t, \lambda_1) \\ \Delta A(t, \lambda_2)\end{bmatrix}
\dfrac{1}{\rho\times dpf}$$

where ΔA(t; λj) (j = 1,2) is the unit-less absorbance (optical density) variation of wavelength λj, αHbX(λj)is the extinction coefficient of HbX in μM−1 mm−1 (note that HbX ∊ {HbO, HbR}), d is the unit-less differential pathlength factor (DPF), and l is the distance (in millimeters) between an emitter and a detector.

```{r}
df_hb <- df_od %>%
  pivot_longer(cols=matches("S\\d*"), names_to="channel", values_to="signal") %>%
  # group_by(channel) %>% 
  mutate(
    distance = channel %l% data.frame(p$channel, p$p),
    w760 = str_detect(channel, "760"),
    signal = signal / (dpf * distance * hbo_760)
  )
  mutate(across(select(matches("S\\d*760")), ~ .x/(dpf * ))

         # mutate(across(where(is.numeric), ~ pass.filt(.x, W=c(0.01,0.7),type="pass")))

df_hb %>%
  mutate(row = as.numeric(rownames(df_od))) %>% 
  select(row, everything()) %>%
  pivot_longer(cols=matches("S\\d*"), names_to="channel", values_to="signal") %>%
  mutate(hb = if_else(str_detect(channel, "760"), "hbr", "hbo")) %>% 
  filter(row > 400 & row < 439) %>% 
  group_by(channel) %>% 
  filter(!any(signal > 0.3)) %>% 
  ggplot() +
  aes(x = row, y = signal, color = hb, group = channel) +
  geom_line() +
  coord_cartesian( clip="off") +
  theme_minimal()

df_hb

```


```{r}
EL = matrix(hb_abs, ncol=2)
iEL = inv(EL)

ModifiedBeerLambertLaw <- function(df) {
  for(i in 1:(length(colnames(df)))) {
    if ((i+1) %% 2 == 0) {
      col_760 = colnames(df)[i]
      col_850 = colnames(df)[i+1]
      
      eval_matrix = t(as.matrix(df_od[c(col_760, col_850)]))
      df_haemo <- as.data.frame(t(as.matrix(iEL %*% eval_matrix))*100000)
      
      df[,col_760] <- df_haemo[,1]
      df[,col_850] <- df_haemo[,2]
    }
  }
  return(as_tibble(df))
}
```

